Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-11-12 Arxiv/main.tex
update laplace accuracy
update laplace accuracy bound

After post-processing, Laplace noise is discretized. Then the accuracy bound for Laplace mechanism is obtained by:
\[
Pr[\lfloor Y \rfloor = t] 
= Pr[ t-1 \leq Y < t] 
= \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t)}{\Delta \bysinfer}}).
\]

Let $\betad(\alpha, \beta)$ be the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism. By applying the accuracy bound into Hellinger distance in our case:
$$
\begin{array}{rcl}
& Pr[\hlg(\bysinfer(\dataobs), r_L ) = \hlg(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)] 
=  \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t)}{\Delta \bysinfer}})\\
\end{array}
$$
where $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor$.\\
By simplification the Hellinger distance in $\hlg(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$, we get:
\begin{itemize}
\item[\textbf{case 1:}] \textbf{t is even}\\

\item[\textbf{case 2:}] \textbf{t is odd}
\end{itemize}

>>>>

After post-processing, Laplace noise is discretized. Then the accuracy bound for Laplace mechanism is obtained by:
\[
Pr\big[\lfloor Y \rfloor = t\big] 
= Pr[ t-1 \leq Y < t] 
= \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t)}{\Delta \bysinfer}}).
\]

Let $\betad(\alpha, \beta)$ be the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism. By applying the accuracy bound into Hellinger distance in our case:
$$
\begin{array}{rcl}
& Pr\big[\hlg(\bysinfer(\dataobs), r_L ) 
= \hlg(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] 
=  \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t)}{\Delta \bysinfer}})\\
\end{array}
$$
where $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.\\
By simplification the Hellinger distance in $\hlg(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$, we get:

\begin{itemize}
  \item[\textbf{case 1:}] \textbf{t is even}\\
  \begin{align*}
  & Pr\Bigg[\hlg(\bysinfer(\dataobs), r_L ) 
  = 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
  \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
  \cdot
  \prod_{k = 1}^{\frac{t}{2}}
  \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}\ \Bigg] \\
  = \quad & \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t)}{\Delta \bysinfer}})\\
  \end{align*}

  \item[\textbf{case 2:}] \textbf{t is odd}\\
  let $t = 2 m + \frac{1}{2}$
  \begin{align*}
   Pr\Bigg[ \hlg(\bysinfer(\dataobs), r_L ) = & \\
  \qquad &
  1 - \frac{1}{\sqrt{1 + \frac{1}{2\alpha}}} \cdot 
  \sqrt{\frac{1}{\alpha + 2m} + \frac{- 2m - 1}{\beta(\alpha + 2m)}} \cdot \\
  \qquad &\cdot 
  \prod_{k = 0}^{m-1}
  \sqrt{(1 + \frac{1}{2(\alpha + k)})
  (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
  } \\
  \qquad & \cdot 
  \prod_{k = 1}^{m} 
  \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})}\ \Bigg] \\
  = \quad & \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t)}{\Delta \bysinfer}})\\
  \end{align*}

\end{itemize}
